Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
using \plucker coordinates, red values \notePE{***}NGH. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

\subsection{General algorithms}
So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
intersection and advancing front method (shortly AFront) to prolong the intersection. From now on, we shall refer to an algorithm made of these components \emph{BIHsearch}. In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}). \emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows the AFront. The version 
\emph{BIHonly} computes AABB together with BIH, but does not use AFront.

>>>>

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
using \plucker coordinates, red values \notePE{***}NGH. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

\subsection{General algorithms}
So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
intersection and advancing front method (shortly AFront) to prolong the intersection. From now on, we shall refer to the algorithm made of these components \emph{BIHsearch}. In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}). \emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows AFront. The version 
\emph{BIHonly} computes AABB together with BIH, but does not use AFront.
